Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-10 paper.qmd
Removed MNIST tSNE plot code which is unnecessary

mnist_scaled_obj <- gen_scaled_data(
  data = tsne_mnist2)
tsne_minst_scaled <- mnist_scaled_obj$scaled_nldr

tsne_plot_mnist <- tsne_minst_scaled |> 
  ggplot(aes(x = tSNE1, 
             y = tSNE2)) + 
  geom_point(alpha=0.1, color = "#000000")

# read the png file from device
left_top_img <- readPNG("figures/mnist/mnist_right_top_img.png", native = TRUE)
center_img <- readPNG("figures/mnist/mnist_middle_img.png", native = TRUE)
right_bottom_img <- readPNG("figures/mnist/mnist_right_bottom_img.png", native = TRUE)

tsne_plot_mnist <- tsne_plot_mnist +
    inset_element(p = left_top_img,
                  left = 1,
                  bottom = 0.85,
                  right = 0,
                  top = 0.95) +
    inset_element(p = center_img,
                  left = 0.8,
                  bottom = 0.5,
                  right = 0,
                  top = 0.6) +
    inset_element(p = right_bottom_img,
                  left = 1,
                  bottom = 0.2,
                  right = 0,
                  top = 0.3)
```

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
```{r}
#| fig-cap: "The $\\gD{}$ layout from tSNE applied for the MNIST digit 1 dataset with defualt (hyper-)parameters. We use our model in the $10\\text{-}D$ space to assess whether this is an accurate representation of data structure present in $10\\text{-}D$, or if it is misleading. The angle of the digit 1 images varies along this structure. Images at the top-right of the $\\gD{}$ layout show the digit 1 angled more to the right, while those at the bottom-right show the digit 1 angled more to the left."
#| label: fig-tsne-best
#| fig-pos: H
#| out-width: 22%
#| eval: false

tsne_plot_mnist
```

>>>>

mnist_scaled_obj <- gen_scaled_data(
  data = tsne_mnist2)
tsne_minst_scaled <- mnist_scaled_obj$scaled_nldr 
```

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
